---
<<<<<<< HEAD
title: "Reproducible Research Assignment 1"
author: "Stuart Coggins"
date: "Sunday, June 14, 2015"
output: html_document
---

```{r}
# Read in data
all.data <- read.csv("activity.csv", sep = ",", header = T);

# Calculate total number of steps per day
total.steps.per.day <- setNames(aggregate(all.data$steps, list(all.data$date), FUN = sum, na.rm = T), c("date", "steps"))

# Histogram of steps per day
hist(total.steps.per.day$steps)

# Median number of steps per day
median(total.steps.per.day$steps);

# Mean number of steps per day
mean(total.steps.per.day$steps);
```


```{r}
# Average daily activity pattern

# Calculate total number of steps per day
average.steps.by.interval <- setNames(aggregate(all.data$steps, list(all.data$interval), FUN = mean, na.rm = T), c("interval", "steps"))

# Time series of interval against average number of steps
plot(x = average.steps.by.interval$interval, y = average.steps.by.interval$steps, type = "l")

# Interval with the largest average number of steps
average.steps.by.interval[which.max(average.steps.by.interval$steps), ]
```



```{r}
# Imputing missing values

# Count number of missing values
sum(is.na(all.data$steps))
```


```{r}
# Fill in the missing values with the mean for that interval

# Join the dataframes together so that the average for each interval is known
all.data.imputed <- merge(all.data, average.steps.by.interval, by = "interval")

# Use a for loop to put the average steps for that interval into the steps column, but only if the value is NA
for (i in 1:nrow(all.data.imputed)) {
 if(is.na(all.data.imputed$steps.x[i])) all.data.imputed$steps.x[i] <- all.data.imputed$steps.y[i] }

# Tidy up data by selecting only the columns of interest and renaming columns where appropriate
all.data.imputed <- all.data.imputed[ , 1:3]
names(all.data.imputed)[2] <- "steps"

# Check if the number of NA rows has changed
sum(is.na(all.data.imputed$steps))
```


```{r}

# Change date datatype to actually be a date rather than character
all.data.imputed$date <- as.POSIXlt(all.data.imputed$date)

# Calculate whether a date fell on a weekend or on a weekday
all.data.imputed$day.type <- as.factor(ifelse(weekdays(all.data.imputed$date) %in% c("Saturday", "Sunday"), "weekend", "weekday"))


# Calculate total number of steps per day by day.type
average.steps.by.interval.and.daytype <- setNames(aggregate(all.data.imputed$steps, list(all.data.imputed$interval, all.data.imputed$day.type), FUN = mean, na.rm = T), c("interval", "day.type", "steps"))

# Load ggplot2 and make plot of interval on x-axis and average steps on y-axis, split by whether the date fell on a weekend or on a weekday
library(ggplot2);
ggplot(data = average.steps.by.interval.and.daytype, aes(interval, steps)) + geom_line() + facet_grid(day.type ~ .);
```

library(knitr)
knit2html("Reproducible Research Assignment 1.Rmd")
=======
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
